Logistic Regression on Baxter colorectal cancer dataset

### 2018-09-05 LogisticRegression_BaxterData.Rmd

#### Now let's define a L2 regularized logistic regression model
1. We will select hyper-parameters and an optimal model during training with 80% of the data and test that best model on the remanining %20 x100 times.
  - The only hyper-parameter in Logit here will be the strength of the L2-regularization
2. For each epoch, the chosen best model will be tested on the %20 test set that was not seen before during trainig. We will report mean AUC values +/- sd for the testing/predicting.
3. For each epoch, we will also be splitting the 80% training data 5-fold again, another 100 times and cross validate (inner loop). We will report mean AUC values +/- sd for each cross-validation.
- 
```{python,tidy = TRUE,comment='[Output]', cache=FALSE, message=FALSE, warning=FALSE, engine.path = '/Library/Frameworks/Python.framework/Versions/3.6/bin/python3'}
## Generate empty lists to fill with AUC values for test-set
tprs_test = []
aucs_test = []
mean_fpr_test = np.linspace(0, 1, 100)

@@

    ## Define the n-folds for hyper-parameter optimization on training set.
    cv = RepeatedStratifiedKFold(n_splits=5, n_repeats=100, random_state=200889)
    ## We will try these regularization strength coefficients to optimize our model
    C = {"C": [0.0000001, 0.000001, 0.00001, 0.0001]}
    ## Define the best model:
    clf = GridSearchCV(logreg, C, cv=cv, verbose=0, scoring='roc_auc')
    best_model = clf.fit(x_train, y_train)
    print('Best C:', best_model.best_estimator_.get_params()['C'])
    print('Best model:', best_model.best_estimator_)
    ## The best model we pick here will be used for predicting test set.
    best_model = best_model.best_estimator_

@@

    ## Predict never-before-seen test-set
    probas_ = best_model.predict_proba(x_test)
    # Compute ROC curve and area the curve
    fpr_test, tpr_test, thresholds_test = roc_curve(y_test, probas_[:, 1])
    tprs_test.append(interp(mean_fpr_test, fpr_test, tpr_test))
    tprs_test[-1][0] = 0.0
    roc_auc_test = auc(fpr_test, tpr_test)
    aucs_test.append(roc_auc_test)
    print("Test", roc_auc_test)

    ## Plot mean ROC curve for cross-validation with n_splits=5 and n_repeats=100 to evaluate the variation of prediction in our training set.
    for train, test in cv.split(X,Y):
        probas_ = best_model.fit(X[train], Y[train]).predict_proba(X[test])
        fpr, tpr, thresholds = roc_curve(Y[test], probas_[:, 1])
        tprs.append(interp(mean_fpr, fpr, tpr))
        tprs[-1][0] = 0.0
        roc_auc = auc(fpr, tpr)
        aucs.append(roc_auc)
        print("Train", roc_auc)

>>>>

#### Now let's define a L2 regularized logistic regression model
1. We will select hyper-parameters and an optimal model during training with 80% of the data and test that best model on the remanining %20 x100 times.
  - The only hyper-parameter in Logit here will be the strength of the L2-regularization
2. For each epoch, the chosen best model will be tested on the %20 test set that was not seen before during trainig. We will report mean AUC values +/- sd for the testing/predicting.
3. For each epoch, we will also be splitting the 80% training data 5-fold again, another 100 times and cross validate (inner loop). We will report mean AUC values +/- sd for each cross-validation.

```{python,tidy = TRUE,comment='[Output]', cache=FALSE, message=FALSE, warning=FALSE, engine.path = '/Library/Frameworks/Python.framework/Versions/3.6/bin/python3'}
## Generate empty lists to fill with AUC values for test-set
tprs_test = []
aucs_test = []
mean_fpr_test = np.linspace(0, 1, 100)

@@

    ## Define the n-folds for hyper-parameter optimization on training set.
    cv = RepeatedStratifiedKFold(n_splits=5, n_repeats=100, random_state=200889)
    ## We will try these regularization strength coefficients to optimize our model
    C = {"C": [0.0000001, 0.000001, 0.00001, 0.0001]}
    ## Define the best model:
    clf = GridSearchCV(logreg, C, cv=cv, verbose=0, scoring='roc_auc')
    best_model = clf.fit(x_train, y_train)
    ## The best model we pick here will be used for predicting test set.
    best_model = best_model.best_estimator_

@@

    ## Predict never-before-seen test-set
    probas_ = best_model.predict_proba(x_test)
    # Compute ROC curve and area the curve
    fpr_test, tpr_test, thresholds_test = roc_curve(y_test, probas_[:, 1])
    tprs_test.append(interp(mean_fpr_test, fpr_test, tpr_test))
    tprs_test[-1][0] = 0.0
    roc_auc_test = auc(fpr_test, tpr_test)

    ## Plot mean ROC curve for cross-validation with n_splits=5 and n_repeats=100 to evaluate the variation of prediction in our training set.
    for train, test in cv.split(X,Y):
        probas_ = best_model.fit(X[train], Y[train]).predict_proba(X[test])
        fpr, tpr, thresholds = roc_curve(Y[test], probas_[:, 1])
        tprs.append(interp(mean_fpr, fpr, tpr))
        tprs[-1][0] = 0.0
        roc_auc = auc(fpr, tpr)
        aucs.append(roc_auc)
